Group meetings

### 2023-06-05 diapo/05-06-23_meeting/main.tex
wrong number was typed
Fixed logos

\documentclass[table]{beamer}
\usetheme{gpmeet}
%\usecolortheme{whale}

\usepackage{tikz}
%\input{shape.tex}

%\usepackage[table]{xcolor}

@@

\logo{
  \begin{tikzpicture}[overlay,remember picture]
    \node[left=0.2cm] at (current page.34){
      \includegraphics[height=1.2cm]{figures/logos}
    };
  \end{tikzpicture}
}

@@

\againframe<3>{prob}
\begin{frame}{Problems/doubts}
  The output is ~0.91 V. This is $-1.1$ and should be $0.015$

@@

\begin{frame}{Networking and sharing}
  \begin{tikzpicture}
    %\node (rect) at (0,0) [rounded corners,draw=text,very thick,minimum width=5.0cm,minimum height=6cm] {};
    %\node (rect) at (6,0) [rounded corners,draw=text,very thick,minimum width=5.0cm,minimum height=6cm] {\raggedleft autre chose };
    \node[draw=text,very thick,rounded corners, text width=0.46\textwidth,minimum height=6cm] at (0,0) {\centering\textbf{Help/Collaboration :}\\ \raggedright \color{text}- If anybody has any idea of an interesting LSTM/NN problem to work on.\\-Also if any phenomen happening are familiar to you, I'll take the help};

    %\end{tikzpicture}
    %\begin{tikzpicture}
    \node[draw=text,very thick,rounded corners, text width=0.46\textwidth,minimum height=6cm] at (0.54\textwidth,0) {\centering\textbf{Recommendations :}\\ \color{text} I worked on a latex/beamer version of the template};
    \end{tikzpicture}
\end{frame}

>>>>

\documentclass[table]{beamer}
\usetheme{gpmeet}

\newcommand{\leftRect}[2]{\node[draw=text,very thick,rounded corners, text width=0.46\textwidth,minimum height=6cm] at (0,0) {\centering\textbf{#1}\\ \raggedright \color{text}#2};}
\newcommand{\rightRect}[2]{\node[draw=text,very thick,rounded corners, text width=0.46\textwidth,minimum height=6cm] at (0.54\textwidth,0) {\centering\textbf{#1}\\ \raggedright \color{text}#2};}

\usepackage{tikz}

@@

\logo{
  \begin{tikzpicture}[overlay,remember picture]
    \node[left=0cm] at (current page.34){
      \includegraphics[height=1cm]{../figures/ist.eps}
      \hspace{1pt}
      \includegraphics[height=1cm]{figures/inesc-mn.png}
      \includegraphics[height=1cm]{../figures/inesc-id.eps}
    };
  \end{tikzpicture}
}

@@

\againframe<3>{prob}
\begin{frame}{Problems/doubts}
  The output is ~0.791 V. This is $-1.09$ and should be $0.015$

@@

\begin{frame}{Networking and sharing}
  \begin{tikzpicture}
    \leftRect{Help/Collaboration :}{- If anybody has any idea of an interesting LSTM/NN problem to work on.\\-Also if any phenomen happening are familiar to you, I'll take the help}

    \rightRect{Recommendations :}{I worked on a latex/beamer version of the template}
  \end{tikzpicture}
\end{frame}

### 2023-06-05 diapo/groupTemplate/main.tex
Template finished
Fixed logos

\begin{frame}{Networking and sharing}

  \begin{tikzpicture}
    \node (rect) at (0,0) [rounded corners,draw=text,very thick,minimum width=5.0cm,minimum height=6cm] {Help/collaboration};
    \node (rect) at (6,0) [rounded corners,draw=text,very thick,minimum width=5.0cm,minimum height=6cm] {\raggedleft autre chose };
  \end{tikzpicture}
\end{frame}

>>>>

\begin{frame}{Networking and sharing}
  \begin{tikzpicture}
    \leftRect{Help/Collaboration :}{- If anybody has any idea of an interesting LSTM/NN problem to work on.\\-Also if any phenomen happening are familiar to you, I'll take the help}
    \rightRect{Recommendations :}{I worked on a latex/beamer version of the template}
  \end{tikzpicture}
\end{frame}
